### 2022-01-21 input/introduction.tex
figure with colors, removing pdf
starting with xas, small changes here and there
pass on introduction

In recent years, the data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT) spread across the different \processes
composing the infrastructure~\cite{maymounkov2002kademlia}. When a
client wants to access specific content, it requests a remote \process
to provide at least one \process identity to retrieve this content
from. After it retrieved the content, the client can create another
replica to improve the performance of future accesses, but it must
contact the indexing service again to notify of the creation of this
new replica.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

\noindent In this paper, we address these issues and limitations
regarding content indexing. Our contribution is threefold:

@@

\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
  empirically support our complexity analysis and the scalability of
  \NAME. Using scoped broadcast, \NAME quickly disseminate messages to
  a subset of relevant \processes. The higher the number of
  partitions, the smaller \NAME's overhead.  Most importantly, \NAME
  does not generate traffic in quiescent systems.  % Our experiments
  %  also highlight the relevance of \NAME in autonomous systems.
  \NAME would allow to lock down the traffic generated by content
  indexing, even in contexts where \emph{physical} partitioning may
  occur.
  %As such, \NAME can constitute a new building block for
  % geo-distributed services.
\end{asparadesc}

@@

The rest of this paper is organized as
follows. Section~\ref{sec:background} illustrates the motivation and
problem behind our proposal.  Section~\ref{sec:adaptive} describes
dynamic consistent partitioning and its implementation along with an
analysis of its complexity. Section~\ref{sec:experimentation} presents
our evaluations.  Section~\ref{sec:related_work} reviews related
work. Finally, Section~\ref{sec:conclusion} concludes and discusses
future work.

>>>>

The data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT) spread across different \processes composing
the infrastructure~\cite{maymounkov2002kademlia}. When a client wants
to access specific content, it requests a remote \process to provide
at least one \process identity to retrieve this content from. After
retrieving the content, the client can create another replica to
improve the performance of future accesses, but it must recontact the
indexing service to notify of the creation of this new replica.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

\noindent In this paper, we address the content indexing challenge as
a distributed partitioning problem. Our contribution is threefold:

@@

\item [$\bullet$] We evaluate \NAME through simulations using
  PeerSim~\cite{montresor2009peersim}. Results show the consistent
  partitioning of the algorithm as well as its scalability. Using
  scoped broadcast, \NAME quickly disseminate messages to a subset of
  relevant \processes. The higher the number of partitions, the
  smaller \NAME's overhead.  Most importantly, \NAME does not generate
  traffic in quiescent systems.  % Our experiments
  %  also highlight the relevance of \NAME in autonomous systems.
  \NAME would allow to lock down the traffic generated by content
  indexing, even in contexts where \emph{physical} partitioning may
  occur.
  %As such, \NAME can constitute a new building block for
  % geo-distributed services.
\end{asparadesc}

@@

The rest of this paper is organized as
follows. Section~\ref{sec:background} illustrates the motivation and
problem behind our proposal.  Section~\ref{sec:adaptive} describes
dynamic consistent partitioning and its
implementation. Section~\ref{sec:experimentation} presents our
evaluations.  Section~\ref{sec:related_work} reviews related
work. Finally, Section~\ref{sec:conclusion} concludes and discusses
future work.
